Verifying Demonstrations

### 2017-10-04 protocol.tex
Adds clarification and fixes typo
Clarifies committing of proof shares

Next we need to consider the protesters' identifiers to prevent Sybil attacks.
\Textcite{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, e.g.\ by 
  \Textcite{Psignatures}, see issue \#27.
}.
Alice has a \ac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets PRF_k(id)\), which is her anonymous 
identity during the protest.

@@

Given the properties of the storage system in \cref{StorageProperties}, 
\cref{CreatedBeforeEnd} is straight-forward: Alice and Bob simply commit their 
proofs to the blockchain as soon as possible after they have participated in the 
protest.
Thus we can infer that a proof (or proof share) was created at the latest when 
it was committed.

>>>>

Next we need to consider the protesters' identifiers to prevent Sybil attacks.
\Textcite{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, e.g.\ by 
  \Textcite{Psignatures}, see issue \#27.
}, where \(n = 1\) in our scenario.
Alice has a \ac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets PRF_k(cid)\), which is her anonymous 
identity during the protest (shown as \(pid\) in \cref{fig:ProofFig}).

@@

The proofs (shares) can be submitted to storage in two steps:
first, committing them to the blockchain; second, to submit all the required 
data.
This will allow some time for computing all the required \ac{NIZK} proofs 
(discussed in the following section).

Given the properties of the storage system in \cref{StorageProperties}, 
\cref{CreatedBeforeEnd} is straight-forward: once a proof share is created it 
should be committed to the blockchain as soon as possible.
Thus we can infer that a proof (or proof share) was created at the latest when 
it was committed.

We note that there are at least two entities who know each proof share, the 
protester and the witness.
Alice and Bob simply commit their proofs (i.e.\ all proof shares of their 
proofs) to the blockchain as soon as possible after they have participated in 
the protest.
The witnesses do the same, they commit all the proof shares that they helped 
create.
(Shown in \cref{fig:ProtocolOverview}.)
